Adversarial Training of Neural Networks\\ against Systematic Uncertainty

### 2016-08-29 tex/paper.tex
save (work in progress)

\begin{algorithm}[t]
\caption{Adversarial training of a classifier $f$ against an adversary $r$.\\
{\it Inputs:} training data $\{ x_i, y_i, \lambda_i \}_{i=1}^N$\\
{\it Outputs:} $\smash{\hat\theta_f}, \smash{\hat\theta_r}$\\
{\it Hyper-parameters:} Number $T$ of training iterations, Number $K$ of gradient steps to update $r$.}
\label{alg:adversarial-training}
\begin{algorithmic}[1]
    \For{$t=1$ to $T$}
        \For{$k=1$ to $K$} \Comment{Update $r$}
            \State{Sample minibatch $\{x_m, \lambda_m \}_{m=1}^M$} of size $M$;
            \State{With $\theta_f$ fixed, update the adversary $r$ by ascending its stochastic gradient
            $$\nabla_{\theta_r} \sum_{m=1}^M \left[ -\sum_{l=1}^{|\Lambda|} 1(\lambda_m = \lambda_l)\log r(f(x_m;\theta_f);\theta_r)_l \right];$$}
        \EndFor
        \State{Sample minibatch $\{x_m, y_m, \lambda_m \}_{m=1}^M$} of size $M$; \Comment{Update $f$}
        \State{With $\theta_r$ fixed, update $f$ by descending its stochastic gradient
        $$\nabla_{\theta_f} \sum_{m=1}^M \left[ \sum_{c=1}^{|{\cal Y}|} 1(y_m = y_c) \log f(x_m;\theta_f)_c -\sum_{l=1}^{|\Lambda|} 1(\lambda_m = \lambda_l)\log r(f(x_m;\theta_f);\theta_r)_l \right];$$}
    \EndFor
\end{algorithmic}
\end{algorithm}

@@

In this section, we show that Algorithm~\ref{alg:adversarial-training} converges
to a classifier $f$ which is a pivotal quantity in the sense of Eqn.~\ref{eqn:criterion}.

>>>>

\begin{algorithm}[t]
\caption{Adversarial training of a classifier $f$ against an adversary $r$.\\
{\it Inputs:} training data $\{ x_i, y_i, \lambda_i \}_{i=1}^N$\\
{\it Outputs:} $\smash{\hat\theta_f}, \smash{\hat\theta_r}$\\
{\it Hyper-parameters:} Number $T$ of training iterations, Number $K$ of gradient steps to update $r$.}
\label{alg:adversarial-training}
\begin{algorithmic}[1]
    \For{$t=1$ to $T$}
        \For{$k=1$ to $K$} \Comment{Update $r$}
            \State{Sample minibatch $\{x_m, \lambda_m \}_{m=1}^M$} of size $M$;
            \State{With $\theta_f$ fixed, update $r$ by ascending its stochastic gradient $\nabla_{\theta_r} E(\theta_f, \theta_r) :=$
            $$\nabla_{\theta_r} \sum_{m=1}^M \left[ -\sum_{\lambda_l \in \Lambda} 1(\lambda_m = \lambda_l)\log r(f(x_m;\theta_f);\theta_r)_l \right];$$}
        \EndFor
        \State{Sample minibatch $\{x_m, y_m, \lambda_m \}_{m=1}^M$} of size $M$; \Comment{Update $f$}
        \State{With $\theta_r$ fixed, update $f$ by descending its stochastic gradient $\nabla_{\theta_f} E(\theta_f, \theta_r) :=$
        $$\nabla_{\theta_f}  \sum_{m=1}^M \left[ \sum_{y_c \in {\cal Y}} 1(y_m = y_c) \log f(x_m;\theta_f)_c -\sum_{\lambda_l \in \Lambda} 1(\lambda_m = \lambda_l)\log r(f(x_m;\theta_f);\theta_r)_l \right];$$}
    \EndFor
\end{algorithmic}
\end{algorithm}

@@

In this section, we show that Algorithm~\ref{alg:adversarial-training} converges
to a classifier $f$ which is a pivotal quantity in the sense of Eqn.~\ref{eqn:criterion}.
Results below are derived in a non-parametric setting, e.g. by assuming
that both $f$ and $r$ have enough capacity. To simplify the presentation,
we also assume the uniform prior
$p(\lambda) = \frac{1}{|\Lambda|}$ for all $\lambda \in \Lambda$, e.g. by
having the same number of training samples for each modality $\lambda$ of
the nuisance parameter.

\begin{proposition}

Let $\theta_f$ be fixed and $\hat\theta_r = \arg \max_{\theta_r} E(\theta_f,
\theta_r)$. If $r(f(x;\theta_f) ; \hat\theta_r )_l = p(\lambda_l| f(X; \theta_f)) = \frac{1}{|\Lambda|}$ for all
$x$ and all $\lambda_l$, then $f$ is a pivotal quantity.

\end{proposition}
